Seismic Hazard Estimation of Northern Iran Using Smoothed Seismicity

### 2016-09-23 response.tex

\comment{8}{%
Pp 10, line 302: " ... subjective decisions and any reasonable choice ...  " I would disagree that these are subjective decisions. My opinion is that you have applied scientific judgment. You clearly need to communicate where judgment is applied; however, \\
- Details about the implementation of the two seismicity rate models (U, R) should be expanded. Are sub-catalogs developed for the five separate regions and then used to develop separate a-grids? Presumably, the separate rate files are then used to compute hazard curves and are summed at each location. \\
-A logic tree would be of great benefit in clarifying how the source models are combined. In particular, it would clarify the weighting from different completeness levels.\\
-Plots of seismicity rates from the R and U models would be of interest and particularly relevant given that the smoothed seismicity model is the main contribution of this work to hazard analyses for Iran.
}

\response{%
Response will be here.
}

\comment{9}{%
Pp 14, line 391 The incorporation of smaller earthquakes $(M<5)$ will have a significant influence on the hazard associated with PGA. Recent papers by Atkinson and others have demonstrated this effect. You may wish to argue that Mmin was chosen based on the expected smallest magnitude capable of causing damage.
}

\response{%
Thanks for the comment. We computed hazard for events $M_w > 4.5$ and modified the text. 
}

@@

\comment{10}{%
Figure 7: Is the magnitude-frequency distribution just a truncated (Mmin, Mmax) GR model? Figure 7 suggests that the MFD may be tapered?
}

\response{%
Yes it is truncated GR model. (Figure caption is not fixed yet.)
}

@@

\comment{1}{%
The authors present uncertainty in their hazard estimate but do not include a more exhaustive logic tree analysis. Effectively, they have two branches: a regional model and uniform model. It appears that they apply the aleatory uncertainty in the ground motion prediction relation to a form of epistemic uncertainty, effectively double counting this uncertainty in the hazard analysis. I would prefer to see a more standard logic tree analysis where multiple GMPEs (or a backbone plus and minus one standard deviation) and uncertainty in a-value, b-value, and Mmax, for example, are considered. Barring this analysis, I would remove figure 10 and references to hazard uncertainty.
}

\response{Response will be here.}

\comment{2}{%
While I think that the regional and uniform models are generally correct within 1.5 degrees of the border, I think that outside of this region, they may be moderately underestimating hazard by not considering sources with 200 km of their region of interest. Their buffer zone for sources is presently 50 km.
}

\response{That right. We increased the buffer zone up to 2 degrees. (Haven't modified the text)}

@@

\comment{3}{%
It would be good if the abstract is more specific about the results. Where is the hazard greatest? What sources contribute to regions of higher hazard?
}
\response{Response will be here.}

\comment{4}{%
In the second paragraph of the introduction, I would include a reference to a figure of the region to help readers less familiar with the area. This figure should also be referred to in subsequent paragraphs. It is probably sufficient to move reference to figure 1 here.
}
\response{Response will be here.}

\comment{5}{%
line 39:   eight        -> eighth
}
\response{Fixed.}

\comment{6}{%
line 55   focuses in -> focuses on
}
\response{Done. Thanks.}

@@

\comment{7}{%
line 56 -> Please be more specific about how your analysis differs from previous analyses.
}
\response{Response will be here.}

\comment{8}{%
line 60 -> Can you be more specific? What are the other indicators?
}
\response{Response will be here.}

\comment{9}{%
line 71 -> Include reference? Include reference.
}
\response{Response will be here.}

\comment{10}{%
line 78 -> reduce -> acknowledge
}
\response{Fixed.}

\comment{11}{%
line 99 -> Is 0.5 degrees enough? To what distance do you do your ground motion calculations? In the western United States, they are done to 200 km. In the central and eastern, they are done to 1000 km. Depending on this value, you should include sources up to this distance from your region of interest.
}
\response{We reanalyze the hazard with 2 degrees buffer zone. (Not modified in the text.)}

\comment{12}{%
line106 -> northeast -> northwest
}
\response{Done. Thanks}

@@

\comment{16}{%
line 192 -> What is the total number of events before and after declustering?
}
\response{Response will be here.}

\comment{17}{%
line 224 -> Why did you use this method? What are the benefits of one or the other?
}
\response{Response will be here.}

\comment{18}{%
line 232 -> It is unclear how you chose Mc. In some cases, it looks like you chose the peak goodness-of-fit value, but in others you did not. Please be more specific about how Mc was chosen.
}
\response{Response will be here.}

\comment{19}{%
line 267 -> add 'and'
}
\response{Added. Thanks.}

@@

\comment{20}{%
line 289 -> You might also cite the 2014 USGS National Model (Petersen et al., 2014) and the Afghanistan seismic hazard maps (Boyd et al, 2007), which include spatial variability in the smoothing parameter.
}
\response{Response will be here.}

\comment{21}{%
line 297 -> provided below -> provided in the next section
}
\response{Fixed.}

\comment{22}{%
line 300 :  allows to draw information -> allows one to draw information 
}
\response{Done.}

@@

\comment{23}{%
line 323 -> Be more specific about how HA3 computes b and Mmax. What is its method?
}
\response{Response will be here.}

\comment{24}{%
line 335 -> Different seismic zone will not necessarily have difference values of b and Mmax. Change to this: Different seismic zone may have different values of b and Mmax.
}
\response{Response will be here.}

\comment{25}{%
line 337 -> a means to reduce epistemic -> a means to account for epistemic 
}
\response{Done.}

\comment{26}{%
line 361 -> lead -> leads
}
\response{Two reviewer suggested two different word. Both of them are correct. Please see.}

\comment{27}{%
line 364 -> How do you address the epistemic uncertainty generally introduced by using a suite of GMPEs?
}
\response{As mentioned in Atkinson and Adam (2013) and Atkinson et al (2014), using different GMPEs with different logic tree weights from different literature is not necessarily the best way to model the epistemic uncertainty in GMPEs. We prefer to use the alternative GMPEs and applicable data to guide the choice of a representative or ?central? GMPE, and to define representative (upper and lower) GMPEs that express uncertainty about the central GMPE. In the previeous study (Khodaverdian 2016), they used Akkar and Bommer (2010) and Ghasemi et al (2009) along side other equations. Akkar and Bommer (2010) derived the equation up to 100 Km, which they used for 200 km. Also Ghasemi et al (2009) is presented the coefficients for spectral acceleration not PGA. Of course this alternative method has been a hotly-debated topic, and there is no clear consensus about that, however, the plots of attenuation relationships in different magnitude illustrate the fact that with this approach we can address the epistemic uncertainty in an acceptable range. We totally agree with the reviewer?s comment that presenting the seismic hazard with upper and lower values (Fig 10) to address the epistemic uncertainty could be misleading for the readers. In order to address these concerns, we do the seismic hazard analysis for bigger domain (2 degrees buffer zone) and combine the results according to the logic tree scheme in Fig X.}

\comment{28}{%
line 365: add 'and'
}
\response{Added. Thanks.}

\comment{29}{%
line 370 -> Could you consider other depths to help fill out your range of epistemic uncertainty?
}
\response{The Kalkan and Gulkan (2004) attenuation relationship is originally generated for Turkey. However, in the recent test by Zafarani and Mousavi (2014), it gives acceptable results for PGA. Since the high accuracy achieved by the current depth, and we have no idea how different depth will change the results, we prefer to not to use a parameter without knowing the effects. }

@@

\comment{30}{%
line 371 -> How does this value compare with the models you decided not to use?
}
\response{Response will be here.}

\comment{31}{%
line 376 -> In this case, you should consider all sources with 200 km of your area of interest.
}
\response{We modified the buffer zone. Thanks.}

\comment{32}{%
line 394:  50-years -> 50-year
}
\response{Done.}

\comment{33}{%
line 420 -> with concentration -> with a concentration
}
\response{Added. Thanks.}

@@

\comment{36}{%
line 431 -> I'm not sure I quite understand this. The standard deviation in the attenuation relation is considered aleatory uncertainty and is present within the hazard curve. Adding it as epistemic as well will cause double counting. If you want to include figure 10, a proper logic tree analysis to include more forms of epistemic uncertainty should be performed. For example, add branches for uncertainty in which GMPE you choose, uncertainty in b-value, uncertainty in Mmax, uncertainty in a-value, uncertainty in smoothing parameter, etc.
}
\response{Response will be here.}

\comment{37}{%
line 434 -> Just because the basic pattern appears to better follow faults in the region does not mean it's a better assessment, especially if the b-values are truly different between regions and better represented by the regional analysis.
}
\response{Response will be here.}

\comment{38}{%
line 439: of city of Tabriz -> of the city of Tabriz.
}
\response{Response will be here.}

\comment{39}{%
line 450 ->  for 2 and 10\%, respectively -> for 2 and 10\% in 50 years, respectively.
}
\response{Response will be here.}

@@

\comment{55}{%
p 26 ? table3 -> Specify units.}
\response{Response will be here.}

\comment{56}{%
p32 ? figure 3 -> You should also show events in the buffer zone used to compute hazard.}
\response{Response will be here.}

\comment{57}{%
p34 ? figure 5 -> Which seismic zone corresponds to which color? It looks like either reporting or rates have changed over time. For example, I might argue that the red region was not complete for M3 and above until 2005. }
\response{Response will be here.}

\comment{58}{%
P37: 10 percent of probability $\to$ 10 percent probability }
\response{Response will be here.}

\comment{59}{%
p 39,figure 11: Include horizontal lines indicating 2 and 10\% probability of exceedance in 50 years.}
\response{Included.}

\comment{60}{%
p 41, figure 12: Can you include curves or points for the other studies in Table 3?}
\response{Response will be here.}
